---
title: "Sofia_SNAP_Data"
format: html
editor: visual
---

## Loading Libraries

```{r, echo = FALSE}
library(ipumsr)
library(dplyr)
library(ggplot2)
library(survey)
library(srvyr)  
library(readr)

```

Loading in Data

Data was gathered from IPUMS and below are the variables and indicators taken from microdata pull:

## Variable Description

**Jump to Variable**

1.  [YEAR](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#YEAR) (Census year)

2.  [SAMPLE](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#SAMPLE) (IPUMS sample identifier)

3.  [SERIAL](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#SERIAL) (Household serial number)

4.  [CBSERIAL](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CBSERIAL) (Original Census Bureau household serial number)

5.  [HHWT](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#HHWT) (Household weight)

6.  [CLUSTER](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CLUSTER) (Household cluster for variance estimation)

7.  [STRATA](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#STRATA) (Household strata for variance estimation)

8.  [GQ](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#GQ) (Group quarters status)

9.  [HHINCOME](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#HHINCOME) (Total household income )

10. [FOODSTMP](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#FOODSTMP) (Food stamp recipiency)

11. [LINGISOL](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#LINGISOL) (Linguistic isolation)

12. [CINETHH](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CINETHH) (Access to internet)

13. [CISMRTPHN](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CISMRTPHN) (Smartphone)

14. [CITABLET](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CITABLET) (Tablet or other portable wireless computer)

15. [CIHAND](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CIHAND) (Handheld computer)

16. [CIDATAPLN](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CIDATAPLN) (Cellular data plan for a smartphone or other mobile device)

17. [CIHISPEED](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CIHISPEED) (Broadband (high speed) Internet service such as cable, fiber optic, or DSL service)

18. [CISAT](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CISAT) (Satellite internet service)

19. [CIDIAL](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CIDIAL) (Dial-up service)

20. [CIOTHSVC](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#CIOTHSVC) (Other internet service)

21. [PERNUM](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#PERNUM) (Person number in sample unit)

22. [PERWT](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#PERWT) (Person weight)

23. [SEX](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#SEX) (Sex)

24. [AGE](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#AGE) (Age)

25. [RACE](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#RACE) (Race \[general version\])

26. [RACED](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#RACED) (Race \[detailed version\])

27. [HISPAN](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#HISPAN) (Hispanic origin \[general version\])

28. [HISPAND](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#HISPAND) (Hispanic origin \[detailed version\])

29. [SPEAKENG](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#SPEAKENG) (Speaks English)

30. [HCOVANY](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#HCOVANY) (Any health insurance coverage)

31. [EMPSTAT](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#EMPSTAT) (Employment status \[general version\])

32. [EMPSTATD](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#EMPSTATD) (Employment status \[detailed version\])

33. [LABFORCE](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#LABFORCE) (Labor force status)

34. [OCC](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#OCC) (Occupation)

35. [INCWAGE](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#INCWAGE) (Wage and salary income)

36. [DISABWRK](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#DISABWRK) (Work disability)

37. [DIFFREM](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#DIFFREM) (Cognitive difficulty)

38. [DIFFPHYS](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#DIFFPHYS) (Ambulatory difficulty)

39. [DIFFMOB](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#DIFFMOB) (Independent living difficulty)

40. [DIFFCARE](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#DIFFCARE) (Self-care difficulty)

41. [DIFFSENS](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#DIFFSENS) (Vision or hearing difficulty)

42. [DIFFEYE](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#DIFFEYE) (Vision difficulty)

43. [TRANWORK](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#TRANWORK) (Means of transportation to work)

44. [SPMPOV](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#SPMPOV) (SPM poverty status)

45. [SPMSNAP](https://live.usa.datadownload.ipums.org/web/extracts/usa/2532640/usa_00017.xml?jwt=eyJhbGciOiJSUzI1NiJ9.eyJpc3MiOiJ1bWEiLCJleHAiOjE3NDQ4NTgzNDgsIm5iZiI6MTc0NDg1NzQ0OCwic3ViIjoiZjFkMzEzNjAtMDNmYS0wMTNkLWI3NmMtMDI0MmMwYTgzMDA0IiwiY29sbGVjdGlvbnMiOlsiY3BzIiwibWVwcyIsIm5oaXMiLCJ1c2EiXX0.GxdO5OYP7LXcUgn9nXFORU-0_CZWOZWrUJN2V7kRypMyRP6AnQm2F2i1m1ZJVgqiq3RhsYx1J9s9qVKgOkRqB9ISRn34xTvJK9c9ytkM5Zeibn0jDvO6vJJruf3rMy-NbchN8td_3W0vN9oHqhmybsRzYCWVnU1smb0IXyXHehtPjePzyvTalqdW_-jeB7lVgQlBuBwzTA7Vt4QQk0Y1oHI4SgyWE75BERfp-bW71eYplD5LrqyrxsNxIQTLIQp9Jka0LQ6zCv-UUYTM1IpVFxIhPbqHFVIKaeU2Rzx8yMYUz8RlcsE6OMlnbj4BNced1nN7vnOlYjj4UfnkhiMdZg#SPMSNAP) (SPM unit's Supplemental Nutrition Assistance Program (SNAP) subsidy)

```{r}
ddi <- read_ipums_ddi("raw_data/usa_00017.xml")
ipums_data <- read_ipums_micro(ddi) 
```

```{r}


# 1) Define the full lookup as a little TSV in a string
occ_lookup <- readr::read_tsv(
  "OCC\toccupation
000\tN/A (not applicable)
0010\tChief executives and legislators
0020\tGeneral and operations managers
0040\tAdvertising and promotions managers
0051\tMarketing managers
0052\tSales managers
0060\tPublic relations and fundraising managers
0101\tAdministrative services managers
0102\tFacilities managers
0110\tComputer and information systems managers
0120\tFinancial managers
0135\tCompensation and benefits managers
0136\tHuman resources managers
0137\tTraining and development managers
0140\tIndustrial production managers
0150\tPurchasing managers
0160\tTransportation, storage, and distribution managers
0205\tFarmers, ranchers, and other agricultural managers
0220\tConstruction managers
0230\tEducation and childcare administrators
0300\tArchitectural and engineering managers
0310\tFood service managers
0335\tEntertainment and recreation managers
0340\tLodging managers
0350\tMedical and health services managers
0360\tNatural sciences managers
0410\tProperty, real estate, and community association managers
0420\tSocial and community service managers
0425\tEmergency management directors
0440\tOther managers
0500\tAgents and business managers of artists, performers, and athletes
0510\tBuyers and purchasing agents, farm products
0520\tWholesale and retail buyers, except farm products
0530\tPurchasing agents, except wholesale, retail, and farm products
0540\tClaims adjusters, appraisers, examiners, and investigators
0565\tCompliance officers
0600\tCost estimators
0630\tHuman resources workers
0640\tCompensation, benefits, and job analysis specialists
0650\tTraining and development specialists
0700\tLogisticians
0705\tProject management specialists
0710\tManagement analysts
0725\tMeeting, convention, and event planners
0726\tFundraisers
0735\tMarket research analysts and marketing specialists
0750\tBusiness operations specialists, all other
0800\tAccountants and auditors
0810\tProperty appraisers and assessors
0820\tBudget analysts
0830\tCredit analysts
0845\tFinancial and investment analysts
0850\tPersonal financial advisors
0860\tInsurance underwriters
0900\tFinancial examiners
0910\tCredit counselors and loan officers
0930\tTax examiners and collectors, and revenue agents
0940\tTax preparers
0960\tOther financial specialists
1005\tComputer and information research scientists
1006\tComputer systems analysts
1007\tInformation security analysts
1010\tComputer programmers
1021\tSoftware developers
1022\tSoftware quality assurance analysts and testers
1031\tWeb developers
1032\tWeb and digital interface designers
1050\tComputer support specialists
1065\tDatabase administrators and architects
1105\tNetwork and computer systems administrators
1106\tComputer network architects
1108\tComputer occupations, all other
1200\tActuaries
1220\tOperations research analysts
1240\tOther mathematical science occupations
1305\tArchitects, except landscape and naval
1306\tLandscape architects
1310\tSurveyors, cartographers, and photogrammetrists
1320\tAerospace engineers
1340\tBiomedical and agricultural engineers
1350\tChemical engineers
1360\tCivil engineers
1400\tComputer hardware engineers
1410\tElectrical and electronics engineers
1420\tEnvironmental engineers
1430\tIndustrial engineers, including health and safety
1440\tMarine engineers and naval architects
1450\tMaterials engineers
1460\tMechanical engineers
1520\tPetroleum, mining and geological engineers, including mining safety engineers
1530\tOther engineers
1541\tArchitectural and civil drafters
1545\tOther drafters
1551\tElectrical and electronic engineering technologists and technicians
1555\tOther engineering technologists and technicians, except drafters
1560\tSurveying and mapping technicians
1600\tAgricultural and food scientists
1610\tBiological scientists
1640\tConservation scientists and foresters
1650\tOther life scientists
1700\tAstronomers and physicists
1710\tAtmospheric and space scientists
1720\tChemists and materials scientists
1745\tEnvironmental scientists and specialists, including health
1750\tGeoscientists and hydrologists, except geographers
1760\tPhysical scientists, all other
1800\tEconomists
1821\tClinical and counseling psychologists
1822\tSchool psychologists
1825\tOther psychologists
1840\tUrban and regional planners
1860\tOther social scientists
1900\tAgricultural and food science technicians
1910\tBiological technicians
1920\tChemical technicians
1935\tEnvironmental science and geoscience technicians, and nuclear technicians
1970\tOther life, physical, and social science technicians
1980\tOccupational health and safety specialists and technicians
2001\tSubstance abuse and behavioral disorder counselors
2002\tEducational, guidance, and career counselors and advisors
2003\tMarriage and family therapists
2004\tMental health counselors
2005\tRehabilitation counselors
2006\tCounselors, all other
2011\tChild, family, and school social workers
2012\tHealthcare social workers
2013\tMental health and substance abuse social workers
2014\tSocial workers, all other
2015\tProbation officers and correctional treatment specialists
2016\tSocial and human service assistants
2025\tOther community and social service specialists
2040\tClergy
2050\tDirectors, religious activities and education
2060\tReligious workers, all other
2100\tLawyers, and judges, magistrates, and other judicial workers
2105\tJudicial law clerks
2145\tParalegals and legal assistants
2170\tTitle examiners, abstractors, and searchers
2180\tLegal support workers, all other
2205\tPostsecondary teachers
2300\tPreschool and kindergarten teachers
2310\tElementary and middle school teachers
2320\tSecondary school teachers
2330\tSpecial education teachers
2350\tTutors
2360\tOther teachers and instructors
2400\tArchivists, curators, and museum technicians
2435\tLibrarians and media collections specialists
2440\tLibrary technicians
2545\tTeaching assistants
2555\tOther educational instruction and library workers
2600\tArtists and related workers
2631\tCommercial and industrial designers
2632\tFashion designers
2633\tFloral designers
2634\tGraphic designers
2635\tInterior designers
2636\tMerchandise displayers and window trimmers
2640\tOther designers
2700\tActors
2710\tProducers and directors
2721\tAthletes and sports competitors
2722\tCoaches and scouts
2723\tUmpires, referees, and other sports officials
2740\tDancers and choreographers
2751\tMusic directors and composers
2752\tMusicians and singers
2755\tDisc jockeys, except radio
2770\tEntertainers and performers, sports and related workers, all other
2805\tBroadcast announcers and radio disc jockeys
2810\tNews analysts, reporters, and journalists
2825\tPublic relations specialists
2830\tEditors
2840\tTechnical writers
2850\tWriters and authors
2861\tInterpreters and translators
2862\tCourt reporters and simultaneous captioners
2865\tMedia and communication workers, all other
2905\tOther media and communication equipment workers
3000\tChiropractors
3010\tDentists
3030\tDietitians and nutritionists
3040\tOptometrists
3050\tPharmacists
3090\tPhysicians
3100\tSurgeons
3110\tPhysician assistants
3120\tPodiatrists
3140\tAudiologists
3150\tOccupational therapists
3160\tPhysical therapists
3200\tRadiation therapists
3210\tRecreational therapists
3220\tRespiratory therapists
3230\tSpeech-language pathologists
3245\tOther therapists
3250\tVeterinarians
3255\tRegistered nurses
3256\tNurse anesthetists
3258\tNurse practitioners, and nurse midwives
3261\tAcupuncturists
3270\tHealthcare diagnosing or treating practitioners, all other
3300\tClinical laboratory technologists and technicians
3310\tDental hygienists
3321\tCardiovascular technologists and technicians
3322\tDiagnostic medical sonographers
3323\tRadiologic technologists and technicians
3324\tMagnetic resonance imaging technologists
3330\tNuclear medicine technologists and medical dosimetrists
3401\tEmergency medical technicians
3402\tParamedics
3421\tPharmacy technicians
3422\tPsychiatric technicians
3423\tSurgical technologists
3424\tVeterinary technologists and laboratory animal caretakers
3430\tDietetic technicians and ophthalmic medical technicians
3500\tLicensed practical and licensed vocational nurses
3515\tMedical records specialists
3520\tOpticians, dispensing
3545\tMiscellaneous health technologists and technicians
3550\tOther healthcare practitioners and technical occupations
3601\tHome health aides
3602\tPersonal care aides
3603\tNursing assistants
3605\tOrderlies and psychiatric aides
3610\tOccupational therapy assistants and aides
3620\tPhysical therapist assistants and aides
3630\tMassage therapists
3640\tDental assistants
3645\tMedical assistants
3646\tMedical transcriptionists
3647\tPharmacy aides
3648\tVeterinary assistants and laboratory animal caretakers
3649\tPhlebotomists
3655\tOther healthcare support workers
3700\tFirst-line supervisors of correctional officers
3710\tFirst-line supervisors of police and detectives
3720\tFirst-line supervisors of firefighting and prevention workers
3725\tMiscellaneous first-line supervisors, protective service workers
3740\tFirefighters
3750\tFire inspectors
3801\tBailiffs
3802\tCorrectional officers and jailers
3820\tDetectives and criminal investigators
3840\tFish and game wardens and parking enforcement officers
3870\tPolice officers
3900\tAnimal control workers
3910\tPrivate detectives and investigators
3930\tSecurity guards and gaming surveillance workers
3940\tCrossing guards and flaggers
3945\tTransportation security screeners
3946\tSchool bus monitors
3960\tOther protective service workers
4000\tChefs and head cooks
4010\tFirst-line supervisors of food preparation and serving workers
4020\tCooks
4030\tFood preparation workers
4040\tBartenders
4055\tFast food and counter workers
4110\tWaiters and waitresses
4120\tFood servers, nonrestaurant
4130\tDining room and cafeteria attendants and bartender helpers
4140\tDishwashers
4150\tHosts and hostesses, restaurant, lounge, and coffee shop
4160\tFood preparation and serving related workers, all other
4200\tFirst-line supervisors of housekeeping and janitorial workers
4210\tFirst-line supervisors of landscaping, lawn service, and groundskeeping workers
4220\tJanitors and building cleaners
4230\tMaids and housekeeping cleaners
4240\tPest control workers
4251\tLandscaping and groundskeeping workers
4252\tTree trimmers and pruners
4255\tOther grounds maintenance workers
4330\tSupervisors of personal care and service workers
4340\tAnimal trainers
4350\tAnimal caretakers
4400\tGambling services workers
4420\tUshers, lobby attendants, and ticket takers
4435\tOther entertainment attendants and related workers
4461\tEmbalmers, crematory operators, and funeral attendants
4465\tMorticians, undertakers, and funeral arrangers
4500\tBarbers
4510\tHairdressers, hairstylists, and cosmetologists
4521\tManicurists and pedicurists
4522\tSkincare specialists
4525\tOther personal appearance workers
4530\tBaggage porters, bellhops, and concierges
4540\tTour and travel guides
4600\tChildcare workers
4621\tExercise trainers and group fitness instructors
4622\tRecreation workers
4640\tResidential advisors
4655\tPersonal care and service workers, all other
4700\tFirst-line supervisors of retail sales workers
4710\tFirst-line supervisors of non-retail sales workers
4720\tCashiers
4740\tCounter and rental clerks
4750\tParts salespersons
4760\tRetail salespersons
4800\tAdvertising sales agents
4810\tInsurance sales agents
4820\tSecurities, commodities, and financial services sales agents
4830\tTravel agents
4840\tSales representatives of services, except advertising, insurance, financial services, and travel
4850\tSales representatives, wholesale and manufacturing
4900\tModels, demonstrators, and product promoters
4920\tReal estate brokers and sales agents
4930\tSales engineers
4940\tTelemarketers
4950\tDoor-to-door sales workers, news and street vendors, and related workers
4965\tSales and related workers, all other
5000\tFirst-line supervisors of office and administrative support workers
5010\tSwitchboard operators, including answering service
5020\tTelephone operators
5040\tCommunications equipment operators, all other
5100\tBill and account collectors
5110\tBilling and posting clerks
5120\tBookkeeping, accounting, and auditing clerks
5140\tPayroll and timekeeping clerks
5150\tProcurement clerks
5160\tTellers
5165\tOther financial clerks
5220\tCourt, municipal, and license clerks
5230\tCredit authorizers, checkers, and clerks
5240\tCustomer service representatives
5250\tEligibility interviewers, government programs
5260\tFile clerks
5300\tHotel, motel, and resort desk clerks
5310\tInterviewers, except eligibility and loan
5320\tLibrary assistants, clerical
5330\tLoan interviewers and clerks
5340\tNew accounts clerks
5350\tCorrespondence clerks and order clerks
5360\tHuman resources assistants, except payroll and timekeeping
5400\tReceptionists and information clerks
5410\tReservation and transportation ticket agents and travel clerks
5420\tOther information and records clerks
5500\tCargo and freight agents
5510\tCouriers and messengers
5521\tPublic safety telecommunicators
5522\tDispatchers, except police, fire, and ambulance
5530\tMeter readers, utilities
5540\tPostal service clerks
5550\tPostal service mail carriers
5560\tPostal service mail sorters, processors, and processing machine operators
5600\tProduction, planning, and expediting clerks
5610\tShipping, receiving, and inventory clerks
5630\tWeighers, measurers, checkers, and samplers, recordkeeping
5710\tExecutive secretaries and executive administrative assistants
5720\tLegal secretaries and administrative assistants
5730\tMedical secretaries and administrative assistants
5740\tSecretaries and administrative assistants, except legal, medical, and executive
5810\tData entry keyers
5820\tWord processors and typists
5840\tInsurance claims and policy processing clerks
5850\tMail clerks and mail machine operators, except postal service
5860\tOffice clerks, general
5900\tOffice machine operators, except computer
5910\tProofreaders and copy markers
5920\tStatistical assistants
5940\tOther office and administrative support workers
6005\tFirst-line supervisors of farming, fishing, and forestry workers
6010\tAgricultural inspectors
6040\tGraders and sorters, agricultural products
6050\tOther agricultural workers
6115\tFishing and hunting workers
6120\tForest and conservation workers
6130\tLogging workers
6200\tFirst-line supervisors of construction trades and extraction workers
6210\tBoilermakers
6220\tBrickmasons, blockmasons, stonemasons, and reinforcing iron and rebar workers
6230\tCarpenters
6240\tCarpet, floor, and tile installers and finishers
6250\tCement masons, concrete finishers, and terrazzo workers
6260\tConstruction laborers
6305\tConstruction equipment operators
6330\tDrywall installers, ceiling tile installers, and tapers
6355\tElectricians
6360\tGlaziers
6400\tInsulation workers
6410\tPainters and paperhangers
6441\tPipelayers
6442\tPlumbers, pipefitters, and steamfitters
6460\tPlasterers and stucco masons
6515\tRoofers
6520\tSheet metal workers
6530\tStructural iron and steel workers
6540\tSolar photovoltaic installers
6600\tHelpers, construction trades
6660\tConstruction and building inspectors
6700\tElevator installers and repairers
6710\tFence erectors
6720\tHazardous materials removal workers
6730\tHighway maintenance workers
6740\tRail-track laying and maintenance equipment operators
6765\tOther construction and related workers
6800\tDerrick, rotary drill, and service unit operators, and roustabouts, oil, gas, and mining
6825\tSurface mining machine operators and earth drillers
6835\tExplosives workers, ordnance handling experts, and blasters
6850\tUnderground mining machine operators
6950\tOther extraction workers
7000\tFirst-line supervisors of mechanics, installers, and repairers
7010\tComputer, automated teller, and office machine repairers
7020\tRadio and telecommunications equipment installers and repairers
7030\tAvionics technicians
7040\tElectric motor, power tool, and related repairers
7100\tOther electrical and electronic equipment mechanics, installers, and repairers
7120\tElectronic home entertainment equipment installers and repairers
7130\tSecurity and fire alarm systems installers
7140\tAircraft mechanics and service technicians
7150\tAutomotive body and related repairers
7160\tAutomotive glass installers and repairers
7200\tAutomotive service technicians and mechanics
7210\tBus and truck mechanics and diesel engine specialists
7220\tHeavy vehicle and mobile equipment service technicians and mechanics
7240\tSmall engine mechanics
7260\tMiscellaneous vehicle and mobile equipment mechanics, installers, and repairers
7300\tControl and valve installers and repairers
7315\tHeating, air conditioning, and refrigeration mechanics and installers
7320\tHome appliance repairers
7330\tIndustrial and refractory machinery mechanics
7340\tMaintenance and repair workers, general
7350\tMaintenance workers, machinery
7360\tMillwrights
7410\tElectrical power-line installers and repairers
7420\tTelecommunications line installers and repairers
7430\tPrecision instrument and equipment repairers
7510\tCoin, vending, and amusement machine servicers and repairers
7540\tLocksmiths and safe repairers
7560\tRiggers
7610\tHelpers--installation, maintenance, and repair workers
7640\tOther installation, maintenance, and repair workers
7700\tFirst-line supervisors of production and operating workers
7720\tElectrical, electronics, and electromechanical assemblers
7730\tEngine and other machine assemblers
7740\tStructural metal fabricators and fitters
7750\tOther assemblers and fabricators
7800\tBakers
7810\tButchers and other meat, poultry, and fish processing workers
7830\tFood and tobacco roasting, baking, and drying machine operators and tenders
7840\tFood batchmakers
7850\tFood cooking machine operators and tenders
7855\tFood processing workers, all other
7905\tComputer numerically controlled tool operators and programmers
7925\tForming machine setters, operators, and tenders, metal and plastic
7950\tCutting, punching, and press machine setters, operators, and tenders, metal and plastic
8000\tGrinding, lapping, polishing, and buffing machine tool setters, operators, and tenders, metal and plastic
8025\tOther machine tool setters, operators, and tenders, metal and plastic
8030\tMachinists
8040\tMetal furnace operators, tenders, pourers, and casters
8100\tModel makers, patternmakers, and molding machine setters, metal and plastic
8130\tTool and die makers
8140\tWelding, soldering, and brazing workers
8225\tOther metal workers and plastic workers
8250\tPrepress technicians and workers
8255\tPrinting press operators
8256\tPrint binding and finishing workers
8300\tLaundry and dry-cleaning workers
8310\tPressers, textile, garment, and related materials
8320\tSewing machine operators
8335\tShoe and leather workers
8350\tTailors, dressmakers, and sewers
8365\tTextile machine setters, operators, and tenders
8450\tUpholsterers
8465\tOther textile, apparel, and furnishings workers
8500\tCabinetmakers and bench carpenters
8510\tFurniture finishers
8530\tSawing machine setters, operators, and tenders, wood
8540\tWoodworking machine setters, operators, and tenders, except sawing
8555\tOther woodworkers
8600\tPower plant operators, distributors, and dispatchers
8610\tStationary engineers and boiler operators
8620\tWater and wastewater treatment plant and system operators
8630\tMiscellaneous plant and system operators
8640\tChemical processing machine setters, operators, and tenders
8650\tCrushing, grinding, polishing, mixing, and blending workers
8710\tCutting workers
8720\tExtruding, forming, pressing, and compacting machine setters, operators, and tenders
8730\tFurnace, kiln, oven, drier, and kettle operators and tenders
8740\tInspectors, testers, sorters, samplers, and weighers
8750\tJewelers and precious stone and metal workers
8760\tDental and ophthalmic laboratory technicians and medical appliance technicians
8800\tPackaging and filling machine operators and tenders
8810\tPainting workers
8830\tPhotographic process workers and processing machine operators
8850\tAdhesive bonding machine operators and tenders
8910\tEtchers and engravers
8920\tMolders, shapers, and casters, except metal and plastic
8930\tPaper goods machine setters, operators, and tenders
8940\tTire builders
8950\tHelpers--production workers
8990\tMiscellaneous production workers, including equipment operators and tenders
9005\tSupervisors of transportation and material moving workers
9030\tAircraft pilots and flight engineers
9040\tAir traffic controllers and airfield operations specialists
9050\tFlight attendants
9110\tAmbulance drivers and attendants, except emergency medical technicians
9121\tBus drivers, school
9122\tBus drivers, transit and intercity
9130\tDriver/sales workers and truck drivers
9141\tShuttle drivers and chauffeurs
9142\tTaxi drivers
9150\tMotor vehicle operators, all other
9210\tLocomotive engineers and operators
9240\tRailroad conductors and yardmasters
9265\tOther rail transportation workers
9300\tSailors and marine oilers, and ship engineers
9310\tShip and boat captains and operators
9350\tParking attendants
9365\tTransportation service attendants
9410\tTransportation inspectors
9415\tPassenger attendants
9430\tOther transportation workers
9510\tCrane and tower operators
9570\tConveyor, dredge, and hoist and winch operators
9600\tIndustrial truck and tractor operators
9610\tCleaners of vehicles and equipment
9620\tLaborers and freight, stock, and material movers, hand
9630\tMachine feeders and offbearers
9640\tPackers and packagers, hand
9645\tStockers and order fillers
9650\tPumping station operators
9720\tRefuse and recyclable material collectors
9760\tOther material moving workers
9800\tMilitary officer special and tactical operations leaders
9810\tFirst-line enlisted military supervisors
9825\tMilitary enlisted tactical operations and air/weapons specialists and crew members
9830\tMilitary, rank not specified
9920\tUnemployed, with no work experience in the last 5 years or earlier or never worked
",
  col_names = c("OCC", "occupation")
) |>
  mutate(OCC = as.numeric(OCC))

# 2) Join & bucket into industries
snap_df <- ipums_data |>
  mutate(is.numeric(OCC)) |>
  filter(!is.na(OCC)) |>
  left_join(occ_lookup, by = "OCC") |>
  mutate(
    occ_num = as.numeric(OCC),
    industry = case_when(
      occ_num >=    0 & occ_num <  1000 ~ "Management, Business, Science, and Arts Occupations",
      occ_num >= 1000 & occ_num <  2000 ~ "Computer, Engineering, and Science Occupations",
      occ_num >= 2000 & occ_num <  3000 ~ "Education, Legal, Community Service, Arts, and Media Occupations",
      occ_num >= 3000 & occ_num <  3600 ~ "Healthcare Practitioners and Technical Occupations",
      occ_num >= 3600 & occ_num <  4700 ~ "Service Occupations",
      occ_num >= 4700 & occ_num <  6000 ~ "Sales and Office Occupations",
      occ_num >= 6000 & occ_num <  7000 ~ "Natural Resources, Construction, and Maintenance Occupations",
      occ_num >= 7000 & occ_num <  7700 ~ "Installation, Maintenance, and Repair Occupations",
      occ_num >= 7700 & occ_num <  9000 ~ "Production Occupations",
      occ_num >= 9000 & occ_num <  9920 ~ "Transportation and Material Moving Occupations",
      occ_num == 9920                  ~ "Unemployed, no recent work experience",
      TRUE                              ~ "Other"
    )
  ) |>
  select(-occ_num)

```

```{r}
twenty_23 <- snap_df |>
  filter(YEAR == 2023) |>
  mutate(snap_status = case_when(
    FOODSTMP == 1 ~ "No",                       
    FOODSTMP == 2 ~ "Yes",             
    NA ~ NA
  )) |>
  filter(!is.na(snap_status))

twenty_23 |>
  filter(is.na(snap_status))

table(twenty_23$snap_status)
```

```{r}
snap_design <- twenty_23 |>
  as_survey_design(weights = PERWT)
```

Industry & Occupation

```{r}
snap_rec <- snap_design |>
  filter(snap_status == "Yes")

snap_no_rec <- snap_design |>
  filter(snap_status == "No")
```

```{r}
snap_rec |>
  ggplot(aes(x = industry, fill = snap_status)) + 
  geom_bar(fill = "red") + 
  coord_flip() + 
  labs(title = "SNAP Recipients Industry Distribution") +
  theme_minimal() +
  theme(
    plot.title      = element_text(hjust = 0.5, margin = margin(b = 10)),
    plot.margin     = unit(c(1.5, 1, 1, 1), "cm")
  )

snap_no_rec |>
  ggplot(aes(x = industry, fill = snap_status)) + 
  geom_bar(fill = "blue") + 
  coord_flip() + 
  labs(title = "Non SNAP Recipients Industry Distribution") +
  theme_minimal() +
  theme(
    plot.title      = element_text(hjust = 0.5, margin = margin(b = 10)),
    plot.margin     = unit(c(1.5, 1, 1, 1), "cm")
  )
```

```{r}
#snap
total_snap = nrow(snap_rec)
snap_rec_ind_comp <- snap_rec |>
  group_by(industry) |>
  summarize(
    industry_count   = n(),         
    industry_percent = industry_count / total_snap,
    .groups = "drop"
  )|>
  select(industry, industry_percent) |>
  rename(snap_percent = industry_percent)

#no snap 
total_no_snap = nrow(snap_no_rec)
snap_no_rec_ind_comp <- snap_no_rec |>
  group_by(industry) |>
  summarize(
    industry_count   = n(),         
    industry_percent = industry_count / total_no_snap,
    .groups = "drop"
  ) |>
  select(industry, industry_percent) |>
  rename(no_snap_percent = industry_percent)
  

diff_snap_occ <- snap_rec_ind_comp |>
  left_join(snap_no_rec_ind_comp, by = "industry") |>
  mutate(ind_diff = snap_percent - no_snap_percent)

diff_snap_occ |>
  mutate(ind_diff = round(ind_diff, 2)) |>
  ggplot(aes(x = industry, y = ind_diff)) +
  geom_bar(stat = "identity", fill = "salmon") +
  coord_flip() +
  labs(title = "Industry Percent Composition Differentials for 
                           SNAP and Non-SNAP Recipients") + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 2, margin = margin(b = 5))  ) + 
  geom_text(
    aes(label = ind_diff,
        hjust = ifelse(ind_diff >= 0, -0.1, 1.1)
    ),
    size  = 3,
    color = "black"
  )
  
```

```{r}
diff_snap_occ|>
  select(industry, ind_diff)
```
